Experiences with planning for natural language generation

### 2008-06-19 trunk/Papers/experiences/introduction.tex
changes to author block and introduction

Natural language generation (NLG; \citeauthor{reiter00building} 2000)
is one of the major subfields of natural language processing.  It is
concerned with computing natural language sentences or texts that
convey a given piece of information to the user.  Problems in NLG are
often more complex than their counterparts in parsing \cite{KolStr02},
and indeed efficiency has not traditionally been the main focus of
NLG.  On the other hand, NLG has some obvious parallels with planning:
One tries to change the mental state of the hearer by applying actions
which correspond to uttering words or sentences.  This parallel has a
long tradition in NLG \cite{appelt:planning,young94dpocl}, and there
has recently been a resurgence of interest in applying modern planning
techniques to NLG \cite{Steedman-Petrick:07,KolSto07,benotti08b}.
These new approaches combine an interest in planning as a modelling
tool for natural language with a hope for improved efficiency by
exploiting modern planning algorithms to help with the search.

>>>>

Natural language generation (NLG; \citeauthor{reiter00building}
\citeyear{reiter00building}) is one of the major subfields of natural
language processing, concerned with computing natural language sentences or
texts that convey a given piece of information to the user. Intuitively,
this task can be viewed as a problem involving actions, beliefs, and goals:
an agent communicating with another agent tries to change the mental state
of the hearer by applying actions which correspond to the utterance of
words or sentences. This characterization of NLG suggests obvious parallels
to automated planning---a view which has a long tradition in NLG
\cite{appelt:planning,young94dpocl}.  More recently, there has been a
resurgence of interest in applying modern planning techniques to NLG
\cite{Steedman-Petrick:07,KolSto07,benotti08b}.  While efficiency has not
been the main focus of NLG, problems in NLG are often more complex than
their counterparts in other areas of natural language processing (such as
parsing \cite{KolStr02}), giving rise to computationally challenging
domains. These new approaches combine an interest in planning as a
modelling tool for natural language, with a hope of improved efficiency by
exploiting modern approaches and algorithms.

%Natural language generation (NLG; \citeauthor{reiter00building} 2000)
%is one of the major subfields of natural language processing.  It is
%concerned with computing natural language sentences or texts that
%convey a given piece of information to the user.  Problems in NLG are
%often more complex than their counterparts in parsing \cite{KolStr02},
%and indeed efficiency has not traditionally been the main focus of
%NLG.  On the other hand, NLG has some obvious parallels with planning:
%One tries to change the mental state of the hearer by applying actions
%which correspond to uttering words or sentences.  This parallel has a
%long tradition in NLG \cite{appelt:planning,young94dpocl}, and there
%has recently been a resurgence of interest in applying modern planning
%techniques to NLG \cite{Steedman-Petrick:07,KolSto07,benotti08b}.
%These new approaches combine an interest in planning as a modelling
%tool for natural language with a hope for improved efficiency by
%exploiting modern planning algorithms to help with the search.

%%%%%
%The purpose of this paper is twofold.
